Performance comparison of Dask and Apache Spark on HPC systems \HL{for Neuroimaging}

### 2022-09-12 latex/paper.tex
[ADD] citation for Datalad and SAM.

\subsection{Dataset}
We used BigBrain\cite{Amunts:13}, a 3-D image of the human brain with voxel
intensities ranging from 0 to 65,535. We converted the blocks into the
NIfTI format, a popular format in neuroimaging. We left the NIfTI blocks
uncompressed, resulting in a total data size of \SI{606}{\gibi\byte}. To
evaluate the effect of block size, we split the image into 1000, 2500,
and 5000 files of \SI{606}{\mebi\byte}, \SI{242.4}{\mebi\byte}, and
\SI{121.2}{\mebi\byte}, respectively.
We used the \href{https://github.com/big-data-lab-team/sam}{sam} library to split the image.

We also used the dataset provided by the Consortium for Reliability and
Reproducibility
(\href{http://fcon_1000.projects.nitrc.org/indi/CoRR/html/}{CoRR})
\cite{zuo2014open}, freely available on
\href{https://datasets.datalad.org/?dir=/corr/RawDataBIDS}{DataLad}.
The entire dataset is \SI{379.83}{\gibi\byte}, containing anatomical, diffusion,
and functional images of 1,654 subjects acquired in 35 sites.
We used all 3,491 anatomical images, representing \SI{26.67}{\gibi\byte} overall
(\SI{7.82}{\mebi\byte} per image on average).

>>>>

\subsection{Dataset}
We used BigBrain\cite{Amunts:13}, a 3-D image of the human brain with voxel
intensities ranging from 0 to 65,535. We converted the blocks into the
NIfTI format, a popular format in neuroimaging. We left the NIfTI blocks
uncompressed, resulting in a total data size of \SI{606}{\gibi\byte}. To
evaluate the effect of block size, we split the image into 1000, 2500,
and 5000 files of \SI{606}{\mebi\byte}, \SI{242.4}{\mebi\byte}, and
\SI{121.2}{\mebi\byte}, respectively.
We used the \href{https://github.com/big-data-lab-team/sam}{sam}~{\cite{sam}} library to split the image.

We also used the dataset provided by the Consortium for Reliability and
Reproducibility
(\href{http://fcon_1000.projects.nitrc.org/indi/CoRR/html/}{CoRR})
\cite{zuo2014open}, freely available on
\href{https://datasets.datalad.org/?dir=/corr/RawDataBIDS}{DataLad}~{\cite{DataladDataset}}.
The entire dataset is \SI{379.83}{\gibi\byte}, containing anatomical, diffusion,
and functional images of 1,654 subjects acquired in 35 sites.
We used all 3,491 anatomical images, representing \SI{26.67}{\gibi\byte} overall
(\SI{7.82}{\mebi\byte} per image on average).
